\Huge{Vipassana for Hackers} \\ \large{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-09-29 paper-two/paper-two.tex
Update paper-2
1)added first draft of abstract
2)added tibetean monks reference
3)spelling error

\begin{abstract}
  \todo{add an abstract} This is the abstract. etc. etc.
\end{abstract}

@@

I took my first Vipassana course in 2017. Vipassana meditation was so unlike anything
I had ever experienced before, after the course I was left extremely curious
about what exactly had happened to me during those ten days. For months afterward, I
spent my mornings and evenings wading through the research in the field of
meditation. I was specifically focused on white papers dealing with the effects of a
10-day Vipassana course on the brains of participants. The research in this area
is limited. The quality research which does exist usually uses a sample of highly
experienced meditators rather than beginners and/or self-reports rather than
objective measures.

@@

The DMN is comprised of specific anatomy including portions of the mid-line of the
brain, an evolutionarily primitive area related to memory and emotion, and
structures in the cortex, an evolutionarily recent part of the brain containting the
executive and higher order functions. \cite{defaultnetworkanatomy} These functionally
connected regions are involved in the neurological basis
of the self, considering the mental states of others, remembering the past, and
imagining the future.

@@

>>>>

\begin{abstract}
  Two years ago, I took my first Vipassana course and immediately began researching 
the effects of meditation on the brain. Written below is a summary of the research 
available as well as speculations on what goes on in the brain during a 10-day silent 
Vipassana meditation retreat.
\end{abstract}

@@

I took my first Vipassana course (as taught by S.N. Goenka) in 2017. 
Vipassana meditation was so unlike anything I had ever experienced before, 
after the course I was left extremely curious about what exactly had happened 
to me during those ten days. For months afterward, I spent my mornings and 
evenings wading through the research in the field of meditation. I was specifically 
focused on white papers dealing with the effects of a 10-day Vipassana course on 
the brains of participants. The research in this area is limited. 
The quality research which does exist usually uses a sample of highly 
experienced meditators \cite{tibeteanmonks} rather than beginners and/or self-reports rather than
objective measures.

@@

The DMN is comprised of specific anatomy including portions of the mid-line of the
brain, an evolutionarily primitive area related to memory and emotion, and
structures in the cortex, an evolutionarily recent part of the brain containing the
executive and higher order functions. \cite{defaultnetworkanatomy} These functionally
connected regions are involved in the neurological basis
of the self, considering the mental states of others, remembering the past, and
imagining the future.

@@

\bibitem{tibeteanmonks}
  Alex Hankey
  \url:https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1697747/
  \textit{Studies of Advanced Stages of Meditation in the Tibetan 
           Buddhist and Vedic Traditions. I: A Comparison of General Changes}
   Evid Based Complement Alternat Med. 2006 Dec; 3(4): 513–521.
